\textbf{Response Letter}

### 2018-12-24 doc/aij18/major-revision/experiments.tex
More answers for the response letter

The conclusions we draw from these experiments is that, when the plan horizon is known, learning with few input samples yield action models that contain 95\% of the preconditions and effects of the GTM plus some extra ones as indicated by the values of precision and recall. With unkown plan horizons, on the other hand, the learned models are generally more different from the GTM; while timeouts are the main cause of the drop in the score, we must point out that pure syntax-based metrics are not adequate to evaluate such under-constrained tasks since the phenomenon of \emph{reformulation} occurs and this largely impacts the results. We will provide experimental evidence of this in section \ref{minimal}.

>>>>

The conclusions we draw from these experiments is that, when the plan horizon is known, learning with few input samples yield action models that contain 95\% of the preconditions and effects of the GTM plus some extra ones as indicated by the values of precision and recall. With unknown plan horizons, on the other hand, the learned models are generally more different from the GTM; while timeouts are the main cause of the drop in the score, we must point out that pure syntax-based metrics are not adequate to evaluate such under-constrained tasks since the phenomenon of \emph{reformulation} occurs and this largely impacts the results (we will provide experimental evidence of this in section \ref{minimal}). \textcolor{red}{These results emphatize a relevant feature our approach, the small size of the training set required by \FAMA in comparison with other approaches (see Table \ref{table:models_comparison2}). Unlike extensive-data approaches, our work explores an alternative research direction to learn action models from small amounts of plan traces. This is an important advantage, particularly in domains in which it is costly or impossible to obtain a significant number of training samples.}

### 2018-12-24 doc/aij18/major-revision/letter.tex
More answers for the response letter

\textcolor[rgb]{1.00,0.00,0.50}{\textbf{DIEGO ....}}

@@

\textcolor[rgb]{1.00,0.00,0.50}{\textbf{DIEGO ... TENEMOS QUE VER ESTO ... }}

@@

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
- "Let $\Omega_v = {v_i}_{i=1}^{max_{a\in A} ar(a)}$ be a new set of objects ‚Ä¶" ‚Äì I think "ar(a)" should be "|ar(a)|"
\end{mdframed}

>>>>

\textcolor[rgb]{1.00,0.00,0.50}{That depends on the domain we are trying to learn. Certainly, most planning domains do not need predicates with repeated variables, but in order to ensure the completeness of our learning approach we have opted to include it.}

@@

\textcolor[rgb]{1.00,0.00,0.50}{Removing symmetries would admittedly improve performance for heuristic planners. This removal can be achieved by ensuring the actions are programmed following some order, which can be done via some additional fluents. We think, however, that the compilation scheme should remain as simple and general as possible to facilitate its understanding.
}

\textcolor[rgb]{1.00,0.00,0.50}{Nevertheless, we want to thank the reviewer for the great idea and we will look into adding this optimization to the approach as a compilation option.}

@@

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
- "Let $\Omega_v = {v_i}_{i=1}^{max_{a\in A} ar(a)}$ be a new set of objects "ì I think "$ar(a)$" should be "$|ar(a)|$"
\end{mdframed}

\textcolor[rgb]{1.00,0.00,0.50}{The function $ar(\cdot)$ returns the arity of an action or predicate (the length of its argument list) and is first introduced in the Background section.}
